A forest is more than its trees: haplotypes and inferred ARGs

### 2024-11-08 paper/writeup.tex
added benchmarkingn figs

%\begin{figure}
%	\includegraphics[width=0.9\textwidth]{newplots_wo_ee/simp_vs_ext_tajimasD_runtime_numtrees.pdf}
%    \caption{
%        Two-part figure, showing reduction in number of edges (left) and increase in speed of stats comptuation (right)
%        as a function of number of trees (modulated by sequence length),
%        on reasonably big simulated sequences.
%        For "speed": plot ratio of runtime before/after extending.
%        \label{fig:speed_and_edges}
%    }
%\end{figure}

@@

>>>>

\begin{figure}
    \includegraphics{benchmarks/one_pop_results_ratios}
    \caption{
        Ratio of
        \textbf{(A)} number of edges, and
        \textbf{(B)} runtime for computing Tajima's $D$;
        before and after extending haplotypes.
        For instance, extending haplotypes reduces number of edges by about 50\%
        and statistic computation runtime by about 20\%
        for long sequences.
        Horizontal axis shows sequence length;
        colors show numbers of samples;
        with lines showing averages across replicates.
        The original tree sequence was simulated with an expanding population;
        see text for details. \comment{TODO}
        \label{fig:speed_and_edges}
    }
\end{figure}

@@

\begin{figure}
    \includegraphics{benchmarks/one_pop_results_absolute_values}
    \caption{
        \label{fig:speed_and_edges_absolute}
    }
\end{figure}

\begin{figure}
    \includegraphics{benchmarks/one_pop_results_timing}
    \caption{
        \label{fig:speed_and_edges_timing}
    }
\end{figure}

\begin{figure}
    \includegraphics{benchmarks/constant_pop_results_ratios}
    \caption{
        As in \figref{fig:speed_and_edges} except that
        the original tree sequence was simulated with an constant population;
        see text for details. \comment{TODO}
        \label{fig:speed_and_edges_constant}
    }
\end{figure}

\begin{figure}
    \includegraphics{benchmarks/constant_pop_results_absolute_values}
    \caption{
        \label{fig:speed_and_edges_absolute_constant}
    }
\end{figure}

\begin{figure}
    \includegraphics{benchmarks/constant_pop_results_timing}
    \caption{
        \label{fig:speed_and_edges_timing_constant}
    }
\end{figure}
